### 2024-07-31 conteudo/eval/eval.tex
add base empirical results

The results obtained in Table \ref{tab:bigclone} indicate that our tool is a pessimist. There 
is no negative sample inferred as duplication even for a minimum similarity threshold of 30\%, 
on the other hand, it is bad for identifying code duplications of complex code duplication types, 
that is Medium Type-3 and Weak Type-3/Type-4. As mentioned in Chapter \ref{cha:tool}, if a 
better result is required on these complex code duplication types, it is possible to change 
the code duplication detection method, as it is designed to be a replaceable component in our 
tool, given the limitations.

@@

@@

The results were obtained by randomly selecting ten functions in the AMD Display driver for 
each similarity range and analyzing if they are duplications and which duplication type.

>>>>

The results presented in Table \ref{tab:bigclone} indicate that our tool is a pessimist. There 
is no negative sample inferred as duplication even for a minimum similarity threshold of 30\%, 
on the other hand, it is bad for identifying code duplications of complex code duplication types, 
that is Medium Type-3 and Weak Type-3/Type-4. As mentioned in Chapter \ref{cha:tool}, if a 
better result is required on these complex code duplication types, it is possible to change 
the code duplication detection method, as it is designed to be a replaceable component in our 
tool, given the limitations.

@@

As described in section \ref{sec:metemp} For the evaluation of our proposed tool by our empirical 
analyses, we randomly selected ten function pairs for a variation of ranges of the similarity 
metric computed by our tool. After that, we analyzed if they were duplications, and if yes, 
we judged the duplication type. Table \ref{tab:emp} presents the results obtained by our tool 
in the empirical analyses.

@@

The results presented in Table \ref{tab:emp} indicate that as the similarity metric reduces, 
there is a significant increase in function pairs that are not duplications in the Linux kernel. 
For the ranges 79\%-81\% of similarity or greater, we have a high percentage of code duplications. 
With 69\%-71\% of similarity, the rate goes down to 50\%. With 59\%-61\%, the rate decreases to 20\%.
With 49\%-51\% similarity or lower, we did not find any code duplications.
